Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-06-10 2023/NUMTA/Full paper/NUMTA_2023_MCO.tex
reduce the size of the figures
link replacement

Computations were conducted on the supercomputer ``Lobachevsky'' of the Nizhni Novgorod State University (operating system CentOS 7, control system SLURM). One node of the supercomputer has 2 processors Intel Sandy Bridge E5-2660 2.2 GHz, 64 Gb RAM. One CPU contains 8 cores, i.e., 16 cores are available on one node. To obtain the executable program code the compilers Intel C++ 17.0.0 and python 3.9 were used. Computations were performed with the support of the package scikit-learn 0.24.2 and the optimization software Globalizer \cite{globalizerSystem}.

@@

The second series was aimed to studying the influence of the parameter $\beta$ from (\ref{eq:24}) on number of trials produced by AGS-SP and HV index. Bi-criteria problems were considered where complicated multiextremal two-dimensional random functions \cite{Grishagin2018} were taken as partial criteria. The level curves of some of them are shown in Fig.  \ref{fig:2}. 50 MMCO problems of this type have been solved with the same parameters $r=3, \varepsilon=0.01$ and number $m=50$ of weight coefficient vectors (\ref{eq:11}) for different values of the parameter $\beta$ from the interval $[0,0.1]$. After solving 50 MMCO problems the results were averaged for each separate $\beta$. The change of HV and the number of trials depending on $\beta$ is shown in Fig. \ref{fig:3}.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{fig3}
\caption{Influence of the parameter $\beta$.} \label{fig:3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig4}
\caption{Operational characteristics for dimension 3.} \label{fig:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig5}
\caption{Operational characteristics for dimension 4.} \label{fig:5}
\end{figure}

>>>>

Computations were conducted on the supercomputer ``Lobachevsky'' of the Nizhni Novgorod State University (operating system CentOS 7, control system SLURM). %One node of the supercomputer has 2 processors Intel Sandy Bridge E5-2660 2.2 GHz, 64 Gb RAM. One CPU contains 8 cores, i.e., 16 cores are available on one node. 
To obtain the executable program code the compilers Intel C++ 17.0.0 and python 3.9 were used. Computations were performed with the support of the package scikit-learn 0.24.2 and the optimization software Globalizer \cite{globalizerSystem}.

@@

The second series was aimed to studying the influence of the parameter $\beta$ from (\ref{eq:24}) on number of trials produced by AGS-SP and HV index. Bi-criteria problems were considered where complicated multiextremal two-dimensional random functions \cite{Grishagin2015_2} were taken as partial criteria. The level curves of some of them are shown in Fig.  \ref{fig:2}. 50 MMCO problems of this type have been solved with the same parameters $r=3, \varepsilon=0.01$ and number $m=50$ of weight coefficient vectors (\ref{eq:11}) for different values of the parameter $\beta$ from the interval $[0,0.1]$. After solving 50 MMCO problems the results were averaged for each separate $\beta$. The change of HV and the number of trials depending on $\beta$ is shown in Fig. \ref{fig:3}.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig3}
\caption{Influence of the parameter $\beta$.} \label{fig:3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{fig4}
\caption{Operational characteristics for dimension 3.} \label{fig:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{fig5}
\caption{Operational characteristics for dimension 4.} \label{fig:5}
\end{figure}
